Linear and modal analysis applying the FE$^2$ multi-scale method for composite materials.

### 2018-02-07 article.tex
cleaning first part
adding the boundary conditions explanations

\usepackage{amsmath, amsfonts, amsthm, mathrsfs, bm}
\usepackage{siunitx}
\sisetup{retain-zero-exponent}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{standalone}
\usepackage{tikz}
\usetikzlibrary{matrix,backgrounds,calc,shapes,arrows,arrows.meta,fit,positioning}
\usetikzlibrary{chains,shapes.multipart}
\usetikzlibrary{shapes,calc}
\usepackage{xcolor}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat = parens, labelsep = space, font = small}

@@

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%----------------------
\newcommand{\sputnik}{{\ttfamily \fontseries{b}\selectfont SPUTNIK }}
\newcommand{\micro}{{\ttfamily \fontseries{b}\selectfont MICRO }}

@@

%---------------------------------------------------------------------------------------------------
\section{Homogenization methods}

@@

>>>>

\usepackage{amsmath, amsfonts, amsthm, mathrsfs, bm}
\usepackage{siunitx} \sisetup{retain-zero-exponent}
\usepackage{standalone}
\usepackage{tikz}
\usetikzlibrary{matrix, chains, backgrounds, calc, shapes, arrows, arrows.meta, fit, positioning}
\usepackage{pgfplots, pgfplotstable}
\usepackage{xcolor}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat = parens, labelsep = space, font = small}

@@

\bibliographystyle{elsarticle-num}

\newcommand{\sputnik}{{\ttfamily \fontseries{b}\selectfont SPUTNIK }}
\newcommand{\micro}{{\ttfamily \fontseries{b}\selectfont MICRO }}
\newcommand{\fe}{FE$^2$}

%--------------------------------------------------

@@

\section{The \fe multi-scale method}

@@

\subsection{Boundary conditions}

Three types of boundary conditions are often considered at the time \fe method is applied.

\begin{itemize}
\item uniform strain
\item periodics
\item uniform stress
\end{itemize}

\subsubsection{Uniform strain}

\subsubsection{Periodic boundary conditions}

In this conditions we it is ask periodicity for the displacements field and anti-periodicity for the tension on the
surface.
First of all we have to define surfaces where we consider that the periodicity of this fields should happen.
For the two-dimensional square domain that we use in this work it seems reasonable to select the two pair of opposite parallel faces 
as we show on figure~\ref{fig_periodic_square}.
There, we select the points, except those in the corners, with a group nomenclature $\Gamma^+$ and $\Gamma^-$ that they
can be represented as:

\begin{equation}
\Gamma^+ = \{ \bm{x} = (x_1, x_2) \in \Gamma \,\setminus\, (x_1 = \ell_x \,\vee\, x_2 = \ell_y) \,\wedge\,
\bm{x}\neq(0,0) \,\wedge\,  \bm{x}\neq(\ell_x,0) \,\wedge\, \bm{x}\neq(0,\ell_y) \}
\end{equation}
\begin{equation}
\Gamma^- = \{ \bm{x} = (x_1, x_2) \in \Gamma \,\setminus\, (x_1 = 0 \,\vee\, x_2 = 0) \,\wedge\,
  \bm{x}\neq(\ell_x,0) \,\wedge\, \bm{x}\neq(\ell_x,\ell_y) \,\wedge\, \bm{x}\neq(0,\ell_y) \}
\end{equation}

Then for every point $\bm{x}^+ \in \Gamma^+$ we will assign a symmetric point $\bm{x}^- \in \Gamma^-$ that will we in
the nearest point on the opposite face of the square as we show in figure~\ref{fig_periodic_square}.

By this way the periodic condition for the displacement field on the surface will be state as:

\begin{equation}
\bm{u}^+ - \bm{u}^- = \overline{\bm{\epsilon}} (\bm{x}^+ - \bm{x}^-),
\end{equation}

\noindent
and the condition for the anti-periodic tractions will be:

\begin{equation}
\bm{\sigma}^{+} \cdot\hat{n}^+ + \bm{\sigma}^{-} \cdot\hat{n}^- = 0,
\end{equation}

\noindent
where $\bm{\sigma}^{+} = \bm{\sigma}(\bm{x}^{+})$ and $\bm{\sigma}^{-} = \bm{\sigma}(\bm{x}^{-})$
and $\hat{n}^+ = \hat{n}(\bm{x}^{+})$ and $\hat{n}^- = \hat{n}(\bm{x}^{-})$ the last are the unit normal vectors 
at those point respectively while the product $\bm{\sigma}\cdot\hat{n}$ represents the surface force at that point.

\subsubsection{Uniform stress}

In the next sections we are going to explain how can they be implemented using a FE discretization of the equations.
